Generate Different Noise Levels

### 2020-01-03 noise_cutoffs/generate_differing_noise.Rmd
missed an instance of sliding density

  chunk_perc = purrr::map_dbl(chunk_indices, function(in_index){
    use_density = sliding_density[seq(in_index, min(in_index + 9999, length(sliding_density)))]
    if (max(use_density) > 0) {
      return(stats::quantile(use_density, 0.99))
    } else {
      return(0)
    }
  })

>>>>

  chunk_perc = purrr::map_dbl(chunk_indices, function(in_index){
    use_counts = nz_counts[seq(in_index, min(in_index + 9999, length(nz_counts)))]
    if (max(use_density) > 0) {
      return(stats::quantile(use_density, 0.99))
    } else {
      return(0)
    }
  })
